\protect Connecting every bit of knowledge: \\ The Structure of Wikipedia's first link network

### 2016-03-01 writeup/wikipedia-network.tex
link to online appendix and enhanced figure placement

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ndegree.png}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions.}
  \label{fig:indegree list}
\end{figure}

@@

\subsection{Network Cycles}

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{graphics/2_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. The area of the circles in the figure indicates the number of traversal visits. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts.}
  \label{fig:2-cycles}
\end{figure*}
We identify 2-cycles, meaning a pair of articles with first link pointing to one another.
Of the 11 million articles, 84,000 are 2-cycles. 
The highest ranking 2-cycles by traversal visits tend to be synonyms (or nearly so) rather than distinct, yet connected topics:
``Health Care'' and ``Medical Case Management,'' ``Broadcasting House,'' and ``BBC,'' ``Secondary Education'' and ``Secondary School'' 
(see Fig.~\ref{fig:2-cycles}).

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{graphics/3_cycles.pdf}
  \caption{
\textbf{Highest ranking 3-cycles.}
We identify groups of three articles whose links form a 3-cycle with the 
last article in the group linking back to the first article.
We rank each 3-cycle by the total number of traversal visits to gauge
the most referenced group of three linked articles. 
The area of the circles in the figure indicates the number of traversal visits.}
  \label{fig:3-cycles}
\end{figure*}

@@

>>>>

\begin{figure}[tp!]
  \includegraphics[width=\columnwidth]{graphics/articles_ndegree.png}
  \caption{
    \textbf{Highest Ranking Articles by in-degree.}
    We rank each article by the number of direct first links to the article (in-degree). The highest-ranking articles tend to represent geographical and biological abstractions. A full online appendix of the results and data is available \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.}
  \label{fig:indegree list}
\end{figure}

@@

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{graphics/2_cycles.pdf}
  \caption{
    \textbf{Highest ranking 2-cycles.}
We identify pairs of articles whose first links point to one another, forming
a 2-cycle. We then rank each pair of articles by the total number of 
traversal visits to gauge the most referenced groups of two articles linked
to each other. The area of the circles in the figure indicates the number of traversal visits. We find 2-cycles often capture synonyms or articles representing nearly the 
same concepts as opposed to distinct concepts.}
  \label{fig:2-cycles}
\end{figure*}
\subsection{Network Cycles}

\begin{figure*}[tp!]
  \includegraphics[width=\textwidth]{graphics/3_cycles.pdf}
  \caption{
\textbf{Highest ranking 3-cycles.}
We identify groups of three articles whose links form a 3-cycle with the 
last article in the group linking back to the first article.
We rank each 3-cycle by the total number of traversal visits to gauge
the most referenced group of three linked articles. 
The area of the circles in the figure indicates the number of traversal visits.}
  \label{fig:3-cycles}
\end{figure*}
We identify 2-cycles, meaning a pair of articles with first link pointing to one another.
Of the 11 million articles, 84,000 are 2-cycles. 
The highest ranking 2-cycles by traversal visits tend to be synonyms (or nearly so) rather than distinct, yet connected topics:
``Health Care'' and ``Medical Case Management,'' ``Broadcasting House,'' and ``BBC,'' ``Secondary Education'' and ``Secondary School'' 
(see Fig.~\ref{fig:2-cycles}).

@@

An online appendix containing all of the code and data used can be accessed \href{http://compstorylab.org/share/papers/ibrahim2016a/index.html}{here}.
